---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(simtimer)
```

# simtimer

simtimer in a little R package designed to simplify (and speeding up) calculating time intervals in discrete event simulations. 

Discrete event simulations is a simulation paradigm that is based on the evaluation of events taking place in a time-specific order. Therefore a discrete event simulation calculates many time intervals. simtimer handles dates and times as integers. This makes working with time intervals as easy (and as fast) as subtracting integers.

## Installation

You can install simtimer from `CRAN` or `github` with:

```{r gh-installation, eval = FALSE}
install.packages("simtimer")

# install.packages("devtools")
devtools::install_github("ims-fhs/simtimer")
```

## Example

Simtimer allows transformation between datetimes (POSIXt) and sim_datetimes (integer) with 
`sim_datetime()` and `datetime()`. 

```{r example}
origin_date <- lubridate::ymd_hms("2016-01-01 00:00:00")
my_datetime <-  lubridate::ymd_hms("2016-01-02 01:01:01")
my_simdatetime <- sim_datetime(my_datetime, origin_date)
my_simdatetime
```
```{r}
datetime(my_simdatetime, origin_date)
```

Simtimer allows to manipulate sim_datetimes and extract parts of sim_datetimes with
`sim_time()`, `sim_wday()` and `sim_date()`.

```{r}
sim_time(my_simdatetime)
sim_wday(my_simdatetime, origin_date)
sim_date(my_simdatetime)
```





